Draft-assinment1

### 2017-02-13 Draft-xuezhou-sjb.Rmd
fill the table

| Variable Name    | Data Type         | Description                                                         | Categoriy in Documentation       |
| --------------  | ------------------ | ---------------------------------------------------------------------| --------------------------------|
| NPT4_COMBINE    | Numeric            |average net price for TITLE IV institutions of both public and private.|  Cost                       |
| DEP_STAT_PCT_IND | Numeric           |Percentage of students who are financially independent                |     Cost                        |
| PAR_ED_PCT_1STGEN| Numeric           |Percentage first-generation students                                  |      Sudent Body                |
| MD_FAMINC        | Numeric           |Median family income in real 2015 dollars                             |       Earning                   |
| PCTPELL          | Numeric           |Percentage of undergraduates who receive a Pell Grant                 |        Financial Aid            |
| PCTFLOAN         | Numeric           |Percent of all federal undergraduate students receiving a federal student loan      |  Financial Aid    |
| GRAD_DEBT_MDN    | Numeric           |The median debt for students who have completed                       |   Financial Aid                 |
| WDRAW_DEBT_MDN   | Numeric           |  Continuous                       |    n     |
| MD_EARN_WNE_P6   | Numeric           |  Continuous                       |     n    |
| MD_EARN_WNE_P10  | Numeric           |  Continuous                       |       n  |
| RPY_3YR_RT_SUPP  | Numeric           |  Continuous                       |      n   |
| CDR3             | Numeric           |  Continuous                       | n        |
| variable$qreF    | Factor            |  Categorical                      |  n       |
| variable$ctrF    | Factor            |  Categorical                      |   n      |
| variable$STABBR  | Factor            |  Categorical                      |   n      |
| APPL_SCH_PCT_GE2 | Numeric           |  Continuous                       | Student        |

>>>>

| Variable Name    | Data Type         | Description                                                         | Categoriy in Documentation       |
| --------------  | ------------------ | ---------------------------------------------------------------------| --------------------------------|
| NPT4_COMBINE    | Numeric            |average net price for TITLE IV institutions of both public and private.|  Cost                       |
| DEP_STAT_PCT_IND | Numeric           |Percentage of students who are financially independent                |     Cost                        |
| PAR_ED_PCT_1STGEN| Numeric           |Percentage first-generation students                                  |      Sudent Body                |
| MD_FAMINC        | Numeric           |Median family income in real 2015 dollars                             |       Earning                   |
| PCTPELL          | Numeric           |Percentage of undergraduates who receive a Pell Grant                 |        Financial Aid            |
| PCTFLOAN         | Numeric           |Percent of all federal undergraduate students receiving a federal student loan      |  Financial Aid    |
| GRAD_DEBT_MDN    | Numeric           |The median debt for students who have completed                       |   Financial Aid                 |
| WDRAW_DEBT_MDN   | Numeric           |The median debt for sutdents who have not completed                      |Financial Aid |
| MD_EARN_WNE_P6   | Numeric           |Median income six years after entry                       |     earning   |
| MD_EARN_WNE_P10  | Numeric           |Median income ten years after entry                       |     earning  |
| RPY_3YR_RT_SUPP  | Numeric           |Repayment rate 3 years after entering repayment                       |Repayment   |
| CDR3             | Numeric           |Loan default rate 3 years afer entering repayment                       |Repayment        |
| variable$qreF    | Factor            |Predominant degree offered                      |School       |
| variable$ctrF    | Factor            |Control of institution                      |School     |
| variable$STABBR  | Factor            |State                      |School     |
| APPL_SCH_PCT_GE2 | Numeric           |Percentage of students submitting 2 or more than 2 applications                       | Student        |
